Reducing retrieval error in MAIAC AOD with the `Earth_obs_cleaning` machine-learning workflow: Results from CONUS

### 2023-08-25 writing/CONUS_AOD.qmd
Move the counts of hidden points into a caption.

```{r agreement_plot}
IG(tar_read(agreement.plot.path))
```

>>>>

```{r agreement_plot}
#| fig-cap: !expr caption
caption = with(list(d = agreement.plot.data(dt)), sprintf(
    "Not shown: %s %s and %s %s",
    d[!in.region & comparison == "y.sat", .N],
    "points outside left panel",
    d[!in.region & comparison == "y.ground.pred", .N],
    "points outside right panel"))
IG(tar_read(agreement.plot.path))
```
